---
title: "Project 1 Interaction Effects"
author: ""
date: "10/19/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(readr)
urlfile <- "https://raw.githubusercontent.com/kaus0399/Applied_Regression_Project_1/main/final_data.csv?token=AOLVKLKNI2726S7DAYOONADBQHOCQ"
train <- read_csv(url(urlfile))
```


```{r}
table_and_int_plot <- function(x, y) {
  freq_table <- table(x, y)
  print(freq_table)
  interaction.plot(x, y, train$summedRevenue_log, col = 1:15, cex.axis = 0.6)
}

```


```{r}
table_and_int_plot(train$channelGrouping, train$device.browser)
```


```{r}
model1 <- aov(summedRevenue_log ~ channelGrouping * device.browser, data = train)
summary(model1)
```

not statistically significant

```{r}
table_and_int_plot(train$channelGrouping, train$device.operatingSystem)
```


```{r}
model2 <- aov(summedRevenue_log ~ channelGrouping * device.operatingSystem, data = train)
summary(model2)
```

statistically significant

```{r}
table_and_int_plot(train$channelGrouping, train$device.deviceCategory)
```
```{r}
model3 <- aov(summedRevenue_log ~ channelGrouping * device.deviceCategory, data = train)
summary(model3)
```

not statistically significant

```{r}
table_and_int_plot(train$channelGrouping, train$geoNetwork.continent)
```
```{r}
model4 <- aov(summedRevenue_log ~ channelGrouping * geoNetwork.continent, data = train)
summary(model4)
```

not statistically significant

```{r}
table_and_int_plot(train$device.browser, train$device.operatingSystem)
```
```{r}
model5 <- aov(summedRevenue_log ~ device.browser * device.operatingSystem, data = train)
summary(model5)
```

not statistically significant

```{r}
table_and_int_plot(train$device.browser, train$device.deviceCategory)
```
```{r}
model6 <- aov(summedRevenue_log ~ device.browser * device.deviceCategory, data = train)
summary(model6)
```


not statistically significant

```{r}
table_and_int_plot(train$device.browser, train$geoNetwork.continent)
```
```{r}
model7 <- aov(summedRevenue_log ~ device.browser * geoNetwork.continent, data = train)
summary(model7)
```

not statistically significant

```{r}
table_and_int_plot(train$device.browser, train$trafficSource.source)
```
```{r}
model8 <- aov(summedRevenue_log ~ device.browser * trafficSource.source, data = train)
summary(model8)
```

statistically significant
           
```{r}
table_and_int_plot(train$device.browser, train$trafficSource.medium)
```
```{r}
model9 <- aov(summedRevenue_log ~ device.browser * trafficSource.medium, data = train)
summary(model9)
```

statistically significant

```{r}
table_and_int_plot(train$device.browser, train$gni_cat)
```
```{r}
model10 <- aov(summedRevenue_log ~ device.browser * gni_cat, data = train)
summary(model10)
```

not statistically significant

```{r}
table_and_int_plot(train$device.operatingSystem, train$trafficSource.source)
```
```{r}
model11 <- aov(summedRevenue_log ~ device.operatingSystem * trafficSource.source, data = train)
summary(model11)
```

statistically significant

```{r}
table_and_int_plot(train$device.operatingSystem, train$trafficSource.medium)
```
```{r}
model12 <- aov(summedRevenue_log ~ device.operatingSystem * trafficSource.medium, data = train)
summary(model12)
```

statistically significant

```{r}
table_and_int_plot(train$device.deviceCategory, train$geoNetwork.continent)
```
```{r}
model13 <- aov(summedRevenue_log ~ device.deviceCategory * geoNetwork.continent, data = train)
summary(model13)
```

not statistically significant

```{r}
table_and_int_plot(train$device.deviceCategory, train$trafficSource.source)
```
```{r}
model14 <- aov(summedRevenue_log ~ device.deviceCategory * trafficSource.source, data = train)
summary(model14)
```

not statistically significant

```{r}
table_and_int_plot(train$device.deviceCategory, train$trafficSource.medium)
```
```{r}
model15 <- aov(summedRevenue_log ~ device.deviceCategory * trafficSource.medium, data = train)
summary(model15)
```

not statistically significant

```{r}
table_and_int_plot(train$geoNetwork.continent, train$trafficSource.source)
```
```{r}
model16 <- aov(summedRevenue_log ~ geoNetwork.continent * trafficSource.source, data = train)
summary(model16)
```

not statistically significant

```{r}
table_and_int_plot(train$geoNetwork.continent, train$trafficSource.medium)
```
```{r}
model17 <- aov(summedRevenue_log ~ geoNetwork.continent * trafficSource.medium, data = train)
summary(model17)
```

not statistically significant

```{r}
table_and_int_plot(train$trafficSource.source, train$gni_cat)
```
```{r}
model18 <- aov(summedRevenue_log ~ trafficSource.source * gni_cat, data = train)
summary(model18)
```

not statistically significant

```{r}
table_and_int_plot(train$trafficSource.medium, train$gni_cat)
```
```{r}
model19 <- aov(summedRevenue_log ~ trafficSource.medium * gni_cat, data = train)
summary(model19)
```

not statistically significant

```{r}
library(car)
library(effects)
```

```{r}
lm1 <- lm(summedRevenue_log ~ totals.hits * device.operatingSystem, data = train)
summary(lm1)
plot(allEffects(lm1), layout = c(2, 3))
```


```{r}
lm1 <- lm(summedRevenue_log ~ device.browser * totals.hits, data = train)
summary(lm1)
plot(allEffects(lm1))
```

```{r}
lm2 <- lm(summedRevenue_log ~ device.browser * totals.pageviews, data = train)
summary(lm2)
plot(allEffects(lm2))
```

```{r}
lm3 <- lm(summedRevenue_log ~ device.browser * gni2017, data = train)
summary(lm3)
plot(allEffects(lm3))
```

```{r}
lm4 <- lm(summedRevenue_log ~ device.deviceCategory * totals.hits, data = train)
summary(lm4)
plot(allEffects(lm4))
```

```{r}
lm5 <- lm(summedRevenue_log ~ device.deviceCategory * totals.pageviews, data = train)
summary(lm5)
plot(allEffects(lm5))
```

```{r}
lm6 <- lm(summedRevenue_log ~ geoNetwork.continent * totals.hits, data = train)
summary(lm6)
plot(allEffects(lm6))
```

```{r}
lm7 <- lm(summedRevenue_log ~ geoNetwork.continent * totals.pageviews, data = train)
summary(lm7)
plot(allEffects(lm7))
```

```{r}
lm8 <- lm(summedRevenue_log ~ trafficSource.source * totals.hits, data = train)
summary(lm8)
plot(allEffects(lm8))
```

```{r}
lm9 <- lm(summedRevenue_log ~ trafficSource.source * totals.pageviews, data = train)
summary(lm9)
plot(allEffects(lm9))
```
